\Large Taking uncertainty seriously \newline \normalsize A Bayesian approach to word embedding bias estimation

### 2022-03-20 presentations/presentationBoston/presentationBoston.Rmd
Fixes table

Category | Biased | Hard Debiased | Soft Debiased | Diff |
-------| ------| -------| ----- | --------
Religion | 0.859 | 0.934 | 0.894| 0.075 |
Race | 0.892 | 0.925| 0.985 | 0.033 |
Gender | 0.623 | 0.700 | 0.747 | 0.077 |

>>>>

Category | Biased | Hard Debiased | Diff 
-------| ------| -------| ----- | --------
Religion | 0.859 | 0.934 | 0,141 
Race | 0.892 | 0.925| 0,108 
Gender | 0.623 | 0.700 | 0,377

### 2022-03-20 presentations/presentationBoston/presentationBoston.tex
Fixes table

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-2}{}
\begin{block}{Our neutral words (examples, full list size = ADD)}
\protect\hypertarget{our-neutral-words-examples-full-list-size-add}{}
liquor, pow, ballpark, glitchy, billy, dallas, rip, called, outlooks,
viet, floater, rattlesnake, exports, peruvian, recursion, shortfall,
corrected, amicable, solutions, diagnostic, patently, flops, approx,
percents, lox, catapults, hamburger, engulfed, households, north,
snubbed, playtest
\end{block}

\begin{block}{Our human-related words (examples, full list size = ADD)}
\protect\hypertarget{our-human-related-words-examples-full-list-size-add}{}
switch, studio, stick, soup, sometimes, signal, prior, plant, photo,
path, park, near, menu, latter, grass, clock, wear, walk, visitor, toy,
tissue, throw, talk, speak, sleep, eye, enjoy, blogger, character,
candidate, breakfast, supper, dinner, eat, drink, carry, run, cast, ask,
awake, ear, nose, lunch
\end{block}
\end{frame}

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-6}{}
\begin{block}{No principled interpretation}
\protect\hypertarget{no-principled-interpretation}{}
\begin{longtable}[]{@{}lllll@{}}
\toprule
Category & Biased & Hard Debiased & Soft Debiased & Diff \\
\midrule
\endhead
Religion & 0.859 & 0.934 & 0.894 & 0.075 \\
Race & 0.892 & 0.925 & 0.985 & 0.033 \\
Gender & 0.623 & 0.700 & 0.747 & 0.077 \\
\bottomrule
\end{longtable}

>>>>

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-2}{}
\begin{block}{Our neutral words (examples, full list size = 242)}
\protect\hypertarget{our-neutral-words-examples-full-list-size-242}{}
liquor, pow, ballpark, glitchy, billy, dallas, rip, called, outlooks,
viet, floater, rattlesnake, exports, peruvian, recursion, shortfall,
corrected, amicable, solutions, diagnostic, patently, flops, approx,
percents, lox, catapults, hamburger, engulfed, households, north,
snubbed, playtest
\end{block}

\begin{block}{Our human-related words (examples, full list size = 27)}
\protect\hypertarget{our-human-related-words-examples-full-list-size-27}{}
wear, walk, visitor, toy, tissue, throw, talk, speak, sleep, eye, enjoy,
blogger, character, candidate, breakfast, supper, dinner, eat, drink,
carry, run, cast, ask, awake, ear, nose, lunch
\end{block}
\end{frame}

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-6}{}
\begin{block}{No principled interpretation}
\protect\hypertarget{no-principled-interpretation}{}
\begin{longtable}[]{@{}lllll@{}}
\toprule
Category & Biased & Hard Debiased & Diff & \\
\midrule
\endhead
Religion & 0.859 & 0.934 & 0,141 & \\
Race & 0.892 & 0.925 & 0,108 & \\
Gender & 0.623 & 0.700 & 0,377 & \\
\bottomrule
\end{longtable}
